Drivers of spatial synchrony in giant kelp populations

### 2021-05-05 paper/SupMat.Rnw
new fig

Finally, for a ?low? of species of? parameters $\delta, \mu_1, \mu_2, \sigma$, we displayed the whole distribution of $r_1$, values for each of our tail association cases, to make visual comparisons.

@@

Equations \ref{sym_rbar1} - \ref{sym_rbar2sharp} obviously depend only on $\mu_1-\mu_2$, and not independently on $\mu_1$ and $\mu_2$, ?some? only $\mu_1-\mu_2$ appears in these expressions if $\mu_1$ or $\mu_2$ appear at all. Equation \ref{sym_rbar1} is $\bar r_1$ in the asymmetric? tail association cases. But letting $\beta_1 = b_1 + \eta$ and $\beta_2 = b_2 + \eta$ and substituting into \ref{sym_rbar1}, we get

@@

To see that our various metrics are the same for out left- and right-tail associated noise ?parameters?, let $(b_1,b_2)$ denote our left-tail associated random variable with parameters $\mu_1,\mu_2,\sigma$. Then define $\beta_1 = -b_2 + \mu_1 +\mu_2$, $\beta_2=-b_1+\mu_1+\mu_2$. It is easy to see that $\EX(\beta_1)=\mu_1$, $\EX(\beta_2)=\mu_2$, $\sd(\beta_1)=\sd(\beta_2)=\sigma$, so $\beta_1$ and $\beta_2$ are normally distributed. From there it is easy to see that $\beta_1$ and $beta_2$ are distributed in the same wat as our right-tail associated noise with parameter $\mu_1,\mu_2$, and $\sigma$. Making the substitutions $b_2 = -\beta_1 + \mu_1 + \mu_2$ and $b_1 = -\beta_2 + \mu_1+\mu_2$ in ref{r1distribution}, we get

>>>>

Finally, for a few choices of parameters $\delta, \mu_1, \mu_2, \sigma$, we displayed the whole distribution of $r_1$, values for each of our tail association cases, to make visual comparisons.

@@

Equations \ref{sym_rbar1} - \ref{sym_rbar2sharp} obviously depend only on $\mu_1-\mu_2$, and not independently on $\mu_1$ and $\mu_2$, since only $\mu_1-\mu_2$ appears in these expressions if $\mu_1$ or $\mu_2$ appear at all. Equation \ref{sym_rbar1} is $\bar r_1$ in the asymmetric? tail association cases. But letting $\beta_1 = b_1 + \eta$ and $\beta_2 = b_2 + \eta$ and substituting into \ref{sym_rbar1}, we get

@@

To see that our various metrics are the same for out left- and right-tail associated noise processes, let $(b_1,b_2)$ denote our left-tail associated random variable with parameters $\mu_1,\mu_2,\sigma$. Then define $\beta_1 = -b_2 + \mu_1 +\mu_2$, $\beta_2=-b_1+\mu_1+\mu_2$. It is easy to see that $\EX(\beta_1)=\mu_1$, $\EX(\beta_2)=\mu_2$, $\sd(\beta_1)=\sd(\beta_2)=\sigma$, so $\beta_1$ and $\beta_2$ are normally distributed. From there it is easy to see that $\beta_1$ and $beta_2$ are distributed in the same wat as our right-tail associated noise with parameter $\mu_1,\mu_2$, and $\sigma$. Making the substitutions $b_2 = -\beta_1 + \mu_1 + \mu_2$ and $b_1 = -\beta_2 + \mu_1+\mu_2$ in ref{r1distribution}, we get
